Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-02 paper/paper.tex
polishing abstract

\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are popular tools to
defend local networks against attacks. These systems monitor the
network traffic and flag suspicious behavior. Rule-based \nids\ do
that by checking the network traffic against a set of rules, which
become obsolete as attackers learn new strategies to circumvent
existing defenses. This paper proposes \tname{}, a novel approach to
synthesize rules for rule-based \nids. \tname\ leverages malicious
(positive) and benign (negative) traffic to create rules for new
attacks. \tname{} is organized as a pipeline of three components to
1)~create an over-specified seed rule, 2)~derive plausible rules from
the seed, and 3)~rank plausible rules. We evaluated \tname\ against a
set of 21 network attacks with varios
characteristics. \tname\ performed very well, being capable of
generating the correct rule among the top-3 and top-1 rules of the
ranking, respectively, in \percTopThreeRankingPrefix\ and
\percTopOneRankingPrefix\ of the cases.
\end{abstract}

@@

%\Mar{@Lucas, please look for constant
  %numbers as this *in text* and use macros instead. We do not want to
  %leave inconsistent data in the paper!}
We evaluated \tname\ against \totalAttacks attacks of various kinds, such as 
\Luc{This is already on section V, should it also be here?} Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance} and Privilege
escalation (PESC)~\cite{privilege-escalation}. %\Fix{...}\rui{add few examples}. 
The observed results are encouraging. For 
example, \tname\ ranked the correct rule among the top ten rules in 
\percTopFiveRanking\ of the cases. \rui{to discuss, I find 
this a bit weak.}\Mar{agree. let us try to add more examples and data.}

>>>>

\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are popular tools to
defend local networks against attacks. These systems monitor the
network traffic and flag suspicious behavior. Rule-based \nids\ do
that by checking the network traffic against a set of rules, which
become obsolete as attackers learn new strategies to circumvent
existing defenses. This paper proposes \tname{}, a novel approach to
synthesize rules for rule-based \nids. \tname\ leverages malicious
(positive) and benign (negative) traffic to create rules for new
attacks. \tname{} is organized as a pipeline of three components to
1)~create an over-specified seed rule, 2)~derive plausible rules from
the seed, and 3)~rank plausible rules. We evaluated \tname\ against a
set of 21 network attacks with varios
characteristics. \tname\ was capable of generating the correct rule 
among the top-3 and top-1 rules of the ranking, respectively, in 
\percTopThreeRankingPrefix\ and \percTopOneRankingPrefix\ of the cases.
\end{abstract}

@@

%\Mar{@Lucas, please look for constant
  %numbers as this *in text* and use macros instead. We do not want to
  %leave inconsistent data in the paper!}
We evaluated \tname\ against \totalAttacks attacks of various kinds, such as 
Denial-of-Service (DoS)~\cite{denial-of-service},
Active Reconnaissance (AREC)~\cite{active-reconnaissance} and Privilege
escalation (PESC)~\cite{privilege-escalation}. %\Fix{...}\rui{add few examples}. 
The observed results are encouraging. For 
example, \tname\ ranked the correct rule among the top ten rules in 
\percTopFiveRanking\ of the cases. \rui{should we quote the same numbers as in the abstract?}
